---
title: "SPS-DATA607-ASSIGNMENT-2-RESULTS"
author: "Tage N Singh"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

###**This page provides some sample code and outputs for the Multi-Table Project**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,load-requirements,echo=FALSE,message=FALSE}
library(datasets)
library(ggplot2)
library(dplyr)
library("tidyverse")
library(RMySQL)
```

```{r message=TRUE, warning=TRUE}
mydb = dbConnect(MySQL(),user='localtest',password='Localtest!',dbname='shows',host='localhost')

#**Note** that the credentials are local to this implementation of MySQL

dbListTables(mydb)
```

```{r,forsurvey}

rs = dbSendQuery(mydb, "SELECT * FROM survey")

data = fetch(rs)

df1 <- data.frame(data)

tibble (df1)

```

```{r,fornetflixratings}

rs = dbSendQuery(mydb, "SELECT * FROM netflixratings")

data = fetch(rs)

df2 <- data.frame(data)

tibble(df2)

```

The Following Query uses a **LEFT JOIN** to demonstrate the fields from the survey table that do not have a value in the netflixratings table will be part of the resultant dataset.

```{r,query1}

rs = dbSendQuery(mydb, "SELECT survey.title,
survey.`Very satisfied`,
survey.`Satisfied`,
survey.`Neither satisfied nor dissatisfied`,
survey.`Dissatisfied`,
survey.`Very dissatisfied`,
survey.`did not see this one`,
netflixratings.`rating`,
netflixratings.`release year`,
netflixratings.`ratingDescription`
FROM survey LEFT JOIN netflixratings ON (survey.title = netflixratings.title);")


data = fetch(rs,n=50)

df3 <- data.frame(data)

tibble(df3)

```
The Following Query uses a **INNER JOIN** to demonstrate the fields from the survey table that do not have a value in the netflixratings table will *NOT* be part of the resultant dataset

```{r,query2}
rs = dbSendQuery(mydb, "SELECT survey.title,
survey.`Very satisfied`,
survey.`Satisfied`,
survey.`Neither satisfied nor dissatisfied`,
survey.`Dissatisfied`,
survey.`Very dissatisfied`,
survey.`did not see this one`,
netflixratings.`rating`,
netflixratings.`release year`,
netflixratings.`ratingDescription`
FROM survey INNER JOIN netflixratings ON (survey.title = netflixratings.title);")

data = fetch(rs,n=50)

df4 <- data.frame(data)

tibble(df4)

```

```{r,query3}
rs = dbSendQuery(mydb, "SELECT * from survey")

data = fetch(rs,n=50)

df5 <- data.frame(data)

tibble(df5)

```
Another Query converted to a dataframe showing the INNER JOIN feature of the table join
```{r,query4}
rs = dbSendQuery(mydb, "SELECT survey.title,
survey.`Very satisfied`,
survey.`Total Responses`,
netflixratings.`user rating score`
FROM survey INNER JOIN netflixratings ON (survey.title = netflixratings.title);")

data = fetch(rs,n=50)

df6 <- data.frame(data)

tibble(df6)

```
### This marks the End of this Test Project
