---
title: "SPS-DATA607-ASSIGNMENT-2-1"
author: "Tage N Singh"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

## **MULTI-TABLE SURVEY PROJECT**

#### The survey was designed and published to classmates and Linkedin participants using **SurveyMonkey**
#### The NETFLIX data was provided by **https://www.kaggle.com/**

##### You can participate in the survey by clicking on this link **https://www.surveymonkey.com/r/RGWG7Q7**

##### The native SurveyMonkey results can be viewed with this link (**Note** that the project database updates are manual) **https://www.surveymonkey.com/stories/SM-LBNGF732/**

&nbsp;

##### **The GitHub Repository for this project is located here:**
##### https://github.com/tagensingh/SPS-DATA607-ASSIGNMENT-2.git

&nbsp;

### **The steps to build this project database are as follows:** 
#All required files are in the GitHub Repository provided above.

##### 1. Create a MySQL schema called **"shows"** by executing the **"1-create-shows.sql"** script from within the MySQL DBMS

##### 2. Copy the following files to the MySql/data/shows  directory.(This is the directory where your DBMS would create the datails for the 'shows' database from the script above) - **1-data-add-survey-all.csv** - and - **1-netflix-shows-ratings-all.csv**

##### 3. Create the tables **"survey"**, **"netflixratings"** and populate them by executing the script **"1-add-records-shows-all.sql"**

#___________________________________________________________________________________________________

#**THE DATABASE IS READY FOR USE**

#____________________________________________________________________________________________________

&nbsp;

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,load-requirements,echo=FALSE,message=FALSE}
library(datasets)
library(ggplot2)
library(dplyr)
library("tidyverse")
library(RMySQL)
```

```{r message=TRUE, warning=TRUE}
mydb = dbConnect(MySQL(),user='localtest',password='Localtest!',dbname='shows',host='localhost')

#**Note** that the credentials are local to this implementation of MySQL

dbListTables(mydb)
```


```{r,forsurvey}

rs = dbSendQuery(mydb, "SELECT * FROM survey")

data = fetch(rs)

#dbListFields(mydb, 'survey')

summary (data)

```

```{r,fornetflixratings}

rs = dbSendQuery(mydb, "SELECT * FROM netflixratings")

data = fetch(rs)

#dbListFields(mydb, 'netflixratings')

tibble(data)

```

###The Following Query uses a **Left Outer Join** to demonstrate the fields from the survey table that do not have a value in the netflixratings table

```{r,query1}

rs = dbSendQuery(mydb, "SELECT survey.title,
survey.`Very satisfied`,
survey.`Satisfied`,
survey.`Neither satisfied nor dissatisfied`,
survey.`Dissatisfied`,
survey.`Very dissatisfied`,
survey.`did not see this one`,
netflixratings.`rating`,
netflixratings.`release year`,
netflixratings.`ratingDescription`
FROM survey LEFT JOIN netflixratings ON (survey.title = netflixratings.title);")


data = fetch(rs)

data

```

